Our Title

### 2015-05-07 draft.tex
Replaced Chapter 7 with new Chapter 7 - "Policy Courses of Action if ISIL is successful in developing a nuclear device"

@@

@@

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/fixed_vehicle.png}
                \caption{Fixed  vehicle monitor.}
                \label{fig:fixed_vehicle}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/mobile_cargo.png}
                \caption{Mobile cargo monitor.}
                \label{fig:mobile_cargo}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/perm_train.png}
                \caption{Permanent train monitor.}
                \label{fig:perm_train}
        \end{subfigure}
        \caption{RPM designs and illustrations \cite{Simmons2005}.}\label{fig:RPM_designs}
\end{figure}

@@

The purchasing of nuclear materials, while it could be done on a national level, is much more likely to occur through individuals. The only collection of nation confirmed information on incidents of illicit trafficking and other unauthorized activities involving nuclear and other radioactive material is called the ITDB \subsubsection{???????? what does this acronym stand for?  ?????????} and is maintained by the IAEA. As of 2006, over 1000 incidents of illicit trafficking and other unauthorized activities involving nuclear and other radioactive material has been reported to the IAEA with about 25\% specifically involving nuclear materials \cite{Iaea2007}. A majority of these cases involve highly enriched uranium (no plutonium). One such incident occurred in 1994 when an individual stole 2.972 kg of highly enriched uranium from a nuclear factory \cite{Iaea2007}. See \autoref{fig:seizures} for more information on the location and size of notable seizures.

@@

\chapter{Notes on response to successful weapons development}

Up to this point, the main focus of this policy has been the prevention of ISIL from developing, stealing, or buying a nuclear weapon or RDD.  However, it is necessary to develop a contingency in the unlikely event of failure in which ISIL obtains a weapon.  Unfortunately, the U.S. cannot use the same nuclear strategies it has in the past to deal with a nuclear ISIL.  The main focus of U.S. nuclear policy since the collapse of the Soviet Union has been non-proliferation.  There has not been as strong of a focus on deterring attacks from an adversary that already has nuclear capabilities \cite{Bracken2013}. However, even before the fall of the Soviet Union, deterrent strategies, such as counterforce, counter value, and mutually assured destruction, were tailored to deter an enemy state, not an extremist group.  Deterrence can only happen if the adversarial group/state thinks that the punishment received from the U.S. will outweigh the benefits of detonating a nuclear weapon \cite{kaplan1991wizards}.  It is unlikely that the U.S. will ever be able to make a threat that can deter ISIL.  Unlike the Soviet Union and other nuclear states, ISIL is made up entirely of militants who will die in defense of their religion and their caliph.  Death is not something that members of ISIL, or any other terrorist group, fear; it is something they celebrate.  They believe they will be rewarded in the next life for what actions on earth.  Even the threat of bombing by the U.S. and death will not deter them.  If they have reached the point of weapon acquisition, they have already ignored the United States' threats of massive retaliation and will likely continue to ignore any future threats.  For this reason, deterrence will be ineffective if ISIL acquires a bomb, so the U.S. must focus on other methods of stopping ISIL from detonating the weapon \cite{Sanderson2015}.

Once ISIL has a weapon, the next steps for them will be to develop a method of delivery, pick a target, and deploy and detonate the bomb.  If possible, the first priority of the U.S. should be to locate where ISIL is storing the bomb and destroy it using drone strikes.  However, it is highly improbable that the exact location of the bomb will be known or found using current detection technologies.  Even if it is found, it might be stored underground where drone strikes would not reach it.  Therefore, the more practical strategy for the U.S. will be to try to stop ISIL at each of the previously mentioned steps.   First, the U.S. will need to determine what delivery methods are possible for ISIL.  The U.S. can prevent ISIL from acquiring the necessary components to build more complex delivery system and slow down movement of the bomb.  Then, the U.S. can make predictions about the group's targets based on geographical location from ISIL and try to intercept the bomb before it reaches the target.  If all of that fails and the weapon is deployed, all the U.S. can do is to help minimize the damage.  Then, the U.S. and IAEA must be prepared to collect nuclear forensic data after the detonation in order to acquire data to prevent the construction and deployment of a second bomb.

The first step the U.S. can take after bomb acquisition by ISIL is to cut them off at their delivery method.  Generally, for nuclear powers, delivery methods are described by the nuclear triad: ground based missiles, such as ICBMs, strategic air bombers, and submarine-launched missiles.  However, as North Korea has shown, ground based missiles are not easily implemented.  It is highly unlikely that ISIL will be able to construct a long-range missile that can carry a nuclear weapon or a submarine capable of launching it.  North Korea has spent years trying to build ballistic missiles capable of delivering nuclear weapons over long ranges, and it is still questionable if they are capable of medium range distances \cite{Gladstone2015}.  It is also highly unlikely that any country will sell long-range missiles to ISIL.  As mentioned in \autoref{sec:global_rels} (\enquote{Global Relationships}), even though some nations may sell weapons to ISIL, it is still a low probability.  Also, none of these countries have ICBMs. North Korea and Pakistan do have short-range and some medium-range missiles \cite{Gladstone2015,NuclearThreatInitiative2014}.  Though, it is unlikely that these would be sold to ISIL, these countries should be heavily monitored in the event of bomb acquisition.  Submarine capabilities seem highly unlikely as well since they are more difficult to develop than land based missiles and the land that ISIL currently occupies is land locked.  The third part of the nuclear triad is long-range bombers.  However, few countries have long-range bombers and, of those countries, it is highly improbable that any of them would sell or give ISIL a bomber.  Therefore, the most likely method of delivery would be to ship or carry the bomb to the target depending on the location.

The next step the U.S. can take is to predict the targets and intercept the bomb in transit to those targets.  It is unlikely that ISIL would use a nuclear weapon or RDD on cities in Syria or Iraq that they do not occupy since that would make the city and their resources unusable to them.  The fallout afterwards would also be close enough to hurt them as well.  It is more likely they will attack one of the other 61 countries in the Anti-ISIL Coalition \cite{Wordsworth2015}.  As mentioned earlier in this policy, it can be assumed that ISIL will follow a counter value strategy versus counterforce.  They are more likely to attack one of the population centers in one of these countries.  A major U.S. city would initially seem a primary target, however, due to the geographical distance from ISIL, it seems unlikely.  Since missile delivery is highly improbable, it would have to be shipped to the U.S..  However, there is no direct shipment method from ISIL to the U.S..  So, the bomb would be shipped through multiple ports and pass through multiple nuclear detector systems before reaching a U.S. port.  However, this possibility should not be ignored.  For this reason, if it is even suspected that ISIL has acquired a nuclear weapon, security at all U.S. ports should be increased.  Portal detectors should be used at all major ports and border crossings and at as many smaller ports as possible.  There is also the possibility of the attack of European countries.   However, as with the U.S., it is unlikely that ISIL will be able to ship it directly to any of the countries in Europe without it being detected.  However, another reason that European countries are not likely targets is due to the ideology behind ISIL.  ISIL's main targets are currently other Muslims who do not hold their extremist beliefs.  They are slightly more tolerant of Christians and Jews than \enquote{apostate} Muslims. \cite{Wood2015}  ISIL is therefore more likely to attack another Muslim nation, especially one that is geographically close.  Due to their close proximity and involvement in the Anti-ISIL coalition, Saudi Arabia, Jordan, Turkey and Lebanon are likely targets.  Iran is also another likely target due to its large Shia population.  Due to U.S.-Iranian relations and U.S. sanctions on Iran, it is unlikely that the U.S. and Iran will be able to work together on stopping a bomb from crossing over the Iranian border.  However, for the other countries, the U.S. can assist in monitoring their borders and possibly supply these countries with more advanced nuclear detection equipment.  With the U.S. and other countries in the Anti-ISIL Coalition focusing on these countries and their borders, it may be possible to stop the bomb from being delivered to its intended target.

If the bomb does reach its intended target, all the U.S. can do is try to minimize the damage and prevent a second detonation from happening.  If the U.S. or any other country is able to gather intelligence on where the bomb may be detonated but unable to find and disarm it, the best course of action is to try evacuating the area.  Depending on the country, the local government may or may not accept U.S. assistance in evacuating the area.  However, if the bomb was able to make it past all detection to its intended target, there is little chance that the U.S. or any other government will have any warning on where and when detonation will occur.  Once the bomb has detonated, the U.S. and the IAEA will need to work with the local government in order to collect samples and take the necessary measurements for post-detonation forensics.  Using this data, it may be possible to determine how ISIL obtained the weapon and to determine what signatures to look for in the future.  Hopefully, this information would prevent the acquisition and detonation of a second weapon.

@@

Missing?

>>>>

ITDB - Incident and Trafficking Database

@@

Unfortunately, the U.S. cannot use the same nuclear strategies it has in the past to deal with a nuclear ISIL.  The main focus of U.S. nuclear policy since the collapse of the Soviet Union has been non-proliferation.  There has not been as strong of a focus on deterring attacks from an adversary that already has nuclear capabilities \cite{Bracken2013}. However, even before the fall of the Soviet Union, deterrent strategies, such as counterforce, counter value, and mutually assured destruction, were tailored to deter an enemy state, not an extremist group.  Deterrence can only happen if the adversarial group/state thinks that the punishment received from the U.S. will outweigh the benefits of detonating a nuclear weapon \cite{kaplan1991wizards}.  It is unlikely that the U.S. will ever be able to make a threat that can deter ISIL.  Unlike the Soviet Union and other nuclear states, ISIL is made up entirely of militants who will die in defense of their religion and their caliph.  Death is not something that members of ISIL, or any other terrorist group, fear; it is something they celebrate.  They believe they will be rewarded in the next life for what actions on earth.  Even the threat of bombing by the U.S. and death will not deter them.  If they have reached the point of weapon acquisition, they have already ignored the United States' threats of massive retaliation and will likely continue to ignore any future threats.  For this reason, deterrence will be ineffective if ISIL acquires a bomb, so the U.S. must focus on other methods of stopping ISIL from detonating the weapon \cite{Sanderson2015}.

@@

@@

The purchasing of nuclear materials, while it could be done on a national level, is much more likely to occur through individuals. The only collection of nation confirmed information on incidents of illicit trafficking and other unauthorized activities involving nuclear and other radioactive material is called the Incident and Trafficking Database (ITDB) and is maintained by the IAEA. As of 2006, over 1000 incidents of illicit trafficking and other unauthorized activities involving nuclear and other radioactive material has been reported to the IAEA with about 25\% specifically involving nuclear materials \cite{Iaea2007}. A majority of these cases involve highly enriched uranium (no plutonium). One such incident occurred in 1994 when an individual stole 2.972 kg of highly enriched uranium from a nuclear factory \cite{Iaea2007}. See \autoref{fig:seizures} for more information on the location and size of notable seizures.

@@

\chapter{Policy Courses of Action if ISIL is successful in developing a nuclear device}

Up to this point, the main focus of this policy has been the prevention of ISIL from developing, stealing, or buying a nuclear weapon or RDD.  However, it is necessary to develop a contingency in the unlikely event of failure in which ISIL obtains a weapon.

If ISIL is able to obtain a nuclear weapon or components, the U.S. must be prepared to prevent its use both domestically and against U.S. and allied assets abroad. Ultimately, the U.S. may need to take military action to prevent ISIL from using a nuclear device, most likely either through a raid to recover the device or a precision airstrike. U.S. forces should begin to war-game that scenario now, which is a mission most likely fall to U.S. Special Operations Command (SOCOM) in cooperation with U.S. CENTCOM, whose area of operations includes the territory held by ISIL \cite{U.S.DepartmentofDefense}. SOCOM and CENTCOM should begin to war-game and conduct exercises related to this scenario now to ensure that its operators are fully prepared to destroy an ISIL nuclear capability if the time comes. In addition to military action, other steps can be taken to ensure that the U.S. homeland and U.S. foreign assets are not attacked.

\section{Domestic Protection} \label{sec:domestic_protection}

With any terrorist threat, it is imperative to assess the United States' capacity for the detection and interception of weapons and materials that pose a significant risk to American security. In the context of this section, we specifically consider nuclear weapons and materials that have the potential to be detonated domestically after being smuggled into America. We examine current and past efforts and capabilities to prevent such weapons from entering the U.S. undetected, as well as the possibilities for the development and implementation of better detection technologies.

Two of the relevant governmental organizations regulating domestic borders and security are the Federal Bureau of Investigation (FBI) and the Department of Homeland Security (DHS). Part of the responsibility of these organizations is ensuring the security of the U.S. from both domestic and foreign threats. They coordinate intelligence gathering, threat-response, and evidence collection in support of the justice system. With these goals in mind, a significant portion of their work deals with the monitoring of borders. The Department of Homeland Security alone commands more than 180,000 personnel, operating such sub-groups as the U.S. Coast Guard, U.S. Customs and Border Protection (CBP), and the Immigration and Customs Enforcement (ICE) \cite{Robb2005}. One of the most relevant DHS sub-groups is the Domestic Nuclear Detection Office (DNDO). The DNDO is responsible for the development and deployment of radiation and detection equipment to assist any other federal agency, including the other DHS sub-organizations and the FBI \cite{UnitedStatesGovernmentAccountabilityOffice2013}.

The CPB/AAPA RPM plan outlines a phased implementation approach targeting locations around the U.S. based on their assessed risk. The plan additionally details collaboration with the Pacific Northwest National Lab (PNNL), which is responsible for the development of cutting-edge, harmless, and passive detection systems (illustrated in \autoref{fig:RPM_designs}). In 2005, RPM systems had already been deployed at 14 terminals, with another 18 in construction, and 27 in final design \cite{Simmons2005}.

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/fixed_vehicle.png}
                \caption{Fixed  vehicle monitor.}
                \label{fig:fixed_vehicle}
        \end{subfigure}%
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/mobile_cargo.png}
                \caption{Mobile cargo monitor.}
                \label{fig:mobile_cargo}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \includegraphics[width=\textwidth,scale=1]{./figures/perm_train.png}
                \caption{Fixed train monitor.}
                \label{fig:perm_train}
        \end{subfigure}
        \caption{RPM designs and examples \cite{Simmons2005}.}\label{fig:RPM_designs}
\end{figure}

Eight years after the initial development of the RPM plan, the Office of the Inspector General published a report documenting the progress made in the RPM development with an emphasis on seaports \cite{DepartmentofHomelandSecurityDHS2013}. The document reports 444 active RPMs screening 99\% of inbound containerized cargo at large seaports, with the other 1\% of cargo entering low-volume seaports (this 1\% is presumably not monitored). 
One point of concern outlined in the report is that many RPM devices (up to 10\% at a large port) were no longer being used. Further, given the limited use of funds for the DNDO and CBP, no plans (as of the report in 2013) were put in place to ensure continued use of RPM technology. Recommendations were generated in the report to develop an organization to ensure the continued and efficient use of RPMs at seaports.

This document suggests the aggressive continued advancement of such programs. The continued development of new technologies, as outlined in \autoref{app:tech}, must be exploited for every feasible advancement that can lead to increases in national security. This document suggests a priority-phased plan outlining a strong technological collaboration with government labs, similar to the plan put forth in 2005, in order to develop and deploy the next generation of RPMs \cite{Simmons2005}. Such a plan would be managed by the DNDO and executed by the CPB and AAPA. This plan, however, can only be effective given the successfully executed deployment of any developing technology. Technological failures such as the ASP development program are acceptable so long as workable alternatives exist.

\section{Second Line of Defense}

If ISIL attempts to move a nuclear device once they obtain it, it is possible that the device may be transported on boats. This may allow for detection of the device at port entries. Given the Second Line of Defense's radiation detection equipment at borders, airports, and strategic feeder ports in Russia, former Soviet Union states, and other key countries, the current capabilities of the U.S. NNSA SLD Core Program, described in

\subsection{??????? What section is this referring to ???????????}

\autoref{}, could be modified to limit ISIL's ability to smuggle a nuclear weapon out of its territory \cite{Kilmartin2010}. The same proposed changes to stem the inflow of nuclear materials into ISIL controlled territory would apply here as well. The addition of the Port of Lattakia and the Port of Tartous

\subsection{???????? No Figure 1 provided  ?????????}

(see Figure 1) reduces the threat of overseas delivery of a nuclear weapon.

\section{Protection of U.S. Assets Abroad}

\subsection{Force Protection}

While interception of the shipment would be preferred as discussed in the previous sections, it is not guaranteed, and a layered approach to defense is preferred.  If ISIL does acquire a nuclear weapon or RDD, they will most likely target sites overseas since it is unlikely they will acquire a long range delivery system and long distance transportation to the U.S. will be difficult, if not impossible (See \autoref{sec:domestic_protection}).  For this reason, the area around ISIL territories are high risk target areas.  It must be assumed that any American military bases or ships in these regions could be chosen as a target by ISIL.  Since protecting Americans in this region is the top priority, these bases must be prepared for a possible nuclear or radiological attack.  The current protective measures for the military overseas will be analyzed and updated to protect against a nuclear or radiological threat from ISIL.

On October 2, 2006, the Department of Defense issued Instruction 2000.16, which introduced the Force Protection Condition (FPCON) system.  FPCON is the Department of Defense's official terrorist threat system that identifies the possibility of an attack against a military facility or ship.  It also recommends preventive actions and responses that should be taken by military facilities and ships depending on the threat level.  The FPCON threat level is determined by military intelligence on the likelihood of a terrorist attack and is normally set by the geographical combatant commander for that region \cite{Usd2006}.  Jurisdiction of the Middle East falls under the USCENTCOM Combatant Commander.  Since the FPCON system was set up to be used by any U.S. military installation in the world, if intelligence indicates ISIL has acquired a weapon, it is important that this is communicated to all of the geographical combatant commanders.  However, the highest priority should be placed on communicating this intelligence to the USCENTCOM Combatant Commander so that the appropriate FPCON measures can be taken.

The FPCON system has not changed much since it was issued.  It was supplemented by Instruction 2000.12, which was issued on March 1, 2012 and talks about the DoD Antiterrorism Program \cite{U.S.DepartmentofDefense2013}.  However, it does not significantly change the protective measures assigned by FPCON.  Currently, the FPCON consists of five progressive levels of increasing protective measures.  The levels are FPCON Normal, FPCON Alpha, FPCON Bravo, FPCON Charlie, and FPCON Delta.  FPCON Normal is the lowest threat level which all domestic and foreign bases must remain at all times at the minimum.  Since there is always a global threat of possible terrorist activity, minimum security measures must always be taken, such as routine security posture and access control to the installation.  The next threat level is FPCON Alpha, and it applies when there is an increased threat of terrorist activity against the installation.  The extent and nature of the threat may still be unpredictable.  The measures taken under FPCON Alpha must be possible to maintain indefinitely.  FPCON Bravo applies when the threat of terrorist activity increases and becomes more predictable.  Unlike the FPCON Alpha level, a prolonged period of maintaining FPCON Bravo may affect the operational capabilities of the facility and the relationships with local authorities.  The next level, FPCON Charlie, applies when a terrorist incident occurs or military intelligence indicates that a terrorist action or targeting against some facility is likely.  Maintaining this level for a prolonged period may create hardships and affect activities of the personnel.  The highest level is FPCON Delta.  This level only applies in the immediate area where a terrorist activity has occurred or intelligence indicates that a terrorist attack on that particular facility or ship is imminent.  This level is usually localized only to the applicable facility or ship instead of all bases in a region.  These measures are not intended to be sustained for an extended duration as it essentially shuts down the facility except for protective measures \cite{Usd2006}.

If ISIL acquires nuclear weapons, all military bases in the region around ISIL territory should be placed on FPCON Charlie unless intelligence indicates an imminent threat to a particular facility.  Under Charlie, the facility still needs to run, except with much stricter security measures.  Access to the facility or ship will be limited to only a few entrances with random vehicle searches.  The identity of every visitor must be verified, and there will be random searches of their personal items, such as suitcases, briefcases or packages, as well.  There will also be increased patrols of the facility and possibly the perimeter surrounding the facility with assistance from local authorities.  If possible, public and military roads and public facilities around the perimeter of the base will be closed.  Ships also have some additional measures taken under FPCON Charlie.  Even at FPCON Alpha, in a foreign port, the minimum standoff distance from a Navy ship is 400 feet.  However, under FPCON Charlie, there are also frequent and random searches of the pier.  All public visits are terminated, unauthorized crafts are kept away from the ship, unnecessary vehicles are blocked from entering the port, and if possible, a small boat exclusion zone is established around the ship \cite{Usd2006}.

Even stricter measures are implemented under FPCON Delta as it completely locks down the base or ship when the threat is imminent.  FPCON Delta will only be used if the weapon is detected near a particular ship or base or intelligence indicates ISIL plans on attacking that particular facility or ship.  Under FPCON Delta, all vehicles and their contents will be searched before they can enter the facility.  All personnel entering the base must be positively identified, and all of their personally carried items must be searched without exception.  There will be frequent checks of the exterior of buildings and of parking lots in the base.  All non-essential movement will be restricted.  If not done already and if possible, all public and military roads and facilities will be closed around the perimeter of the base.  At the very least, the military road allowing access to the facility must be closed.  For a ship, only necessary personnel will be permitted topside of the ship and all necessary weapons for defense will be employed.  If possible, the ship will cancel its port visit and leave the port \cite{Usd2006}.

Unfortunately, all of these measures were designed to protect against a conventional or possibly chemical or biological terrorist attack.  They were not planned with nuclear weapons or RDDs in mind.  For this reason, it is this policy's recommendation that additional security measures are added.  For the currently established inspections and searches at these higher threat levels, handheld radiation detection devices should be standard equipment.  The detection devices should be used in conjunction with conventional search methods to search the personal belongings and vehicle of anyone trying to enter the facility. They should also be used for inspections on base.  Also, it may be necessary to have modified FPCON Charlie and Delta levels in case of nuclear attacks as well as the regular threat level measures for a non-nuclear threat.  The measures necessary for a nuclear attack will be unnecessary and somewhat impractical to implement just for a conventional terrorist attack.  So, there should be modified measures in the special case of a nuclear threat.  First, for the modified FPCON Charlie, the restrictions outside of the base should be increased.  It is assumed that if ISIL acquires a weapon, it will be small yield.  According to the Federation of American Scientists, Pakistan was only able to first develop bombs with a maximum yield of about 12 kilotons \cite{FederationofAmericanScientists2002}.  If ISIL develops their own bomb, it is unlikely they will develop as large of a bomb as Pakistan, and if ISIL acquires a bomb through Pakistan or North Korea, it will likely still be a small yield device.  For this reason, if possible, every road and facility that is within a 1 to 1.5 mile radius of the base should be closed.  This will severely minimize the damage to the base if the weapon is detonated outside of this perimeter.  Also, if possible, for ships, the pier should be closed to the public and all non-necessary personnel.  The standoff distance from the ship should be increased to 1 to 1.5 miles as well for the modified FPCON Charlie.  For the modified FPCON Delta, it is assumed that the base will be attacked by a nuclear weapon or RDD.  Hardened bunkers should be constructed, if they do not already exist, before ISIL develops a weapon.  Regular FPCON Delta measures will be followed, but, additionally, all civilian and non-essential personnel should move to these nuclear bunkers.  For ships, the ship should just follow regular FPCON Delta measures and leave the port as soon as possible.  These additional security measures should hopefully minimize the damage and probability of a nuclear attack on a military base in the region.

@@

If ISIL is able to obtain a nuclear weapon, the next steps for them would be to develop a method of delivery, pick a target, and deploy and detonate the bomb.  If possible, the first priority of the U.S. should be to locate where ISIL is storing the bomb and destroy it using drone strikes.  However, it is highly improbable that the exact location of the bomb will be known or found using current detection technologies.  Even if it is found, it might be stored underground where drone strikes would not reach it.  Therefore, the more practical strategy for the U.S. will be to try to stop ISIL at each of the previously mentioned steps.   First, the U.S. will need to determine what delivery methods are possible for ISIL.  The U.S. can prevent ISIL from acquiring the necessary components to build more complex delivery system and slow down movement of the bomb.  Then, the U.S. can make predictions about the group's targets based on geographical location from ISIL and try to intercept the bomb before it reaches the target.  If all of that fails and the weapon is deployed, all the U.S. can do is to help minimize the damage.  Then, the U.S. and IAEA must be prepared to collect nuclear forensic data after the detonation in order to acquire data to prevent the construction and deployment of a second bomb.

\section{If ISIL detonates a nuclear device}

If ISIL is successful in detonating a nuclear device, the U.S. must be prepared to take military action in response, as well as to prevent the detonation of a second device. Depending on the U.S. assessment of the threat posed by ISIL's attack (which is a discussion that must be had at the highest levels), a military response may range from an increased air campaign to U.S. ground force involvement in a campaign to destroy ISIL. Additionally, the U.S. must be prepared to collect forensic data to determine, if possible, if any additional countries were complicit in ISIL acquiring a nuclear device. If another nation aided ISIL, the U.S. should consider military action in response consistent with the recommended declaratory policy in

Section XXX Forensics Policy Section XXX.
